Causal Compatibility Inequalities Admitting of Quantum Violations in the Triangle Scenario

### 2016-11-25 documents/BrazilSlides/slides.tex
Some speaking notes for the talk
added one final slide

\begin{frame}
    \frametitle{Inflation Lemma}
    \begin{lemma}[Inflation Lemma]
    Given $\graph$ and inflation $\graph$':
    \begin{center}
        \begin{tikzpicture}
            \pgfmathsetmacro{\vs}{2.2};
            \pgfmathsetmacro{\hs}{5.2};
            \draw (0*\hs,0*\vs) node[](pn){$\underbrace{\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}}_{\text{compatible with $\graph$}}$};
            \draw (1*\hs,0*\vs) node[](cp){$\bc{\prob[n\mid \Pa[\graph]{n}] \mid n \in \nodes}$};
            \draw (1*\hs,-1*\vs) node[](cp_){$\bc{\prob[n'\mid \Pa[\graph']{n'}] \mid n' \in \nodes'}$};
            \draw (0*\hs,-1*\vs) node[](pn_){$\underbrace{\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}}_{\text{compatible with $\graph'$}}$};
            \draw[very thick, ->] (pn) -- (cp);
            \draw[very thick, ->] (cp) -- (cp_) node [midway, above, sloped]{{\footnotesize define}};
            \draw[very thick, ->] (cp_) -- (pn_);
        \end{tikzpicture}
    \end{center}
    \end{lemma}
\end{frame}

@@

\begin{frame}
    \frametitle{Parameterizing Unitary Group}
    \begin{itemize}
        \item Spengler, Huber and Heismayr \cite{Spengler_2010_Unitary} parameterization of $\s{U}\br{d}$
        \[ \la = \begin{pmatrix}
            \textcolor{Blue}{\la_{1,1}} & \textcolor{OliveGreen}{\cdots} & \textcolor{OliveGreen}{\la_{1, d}} \\
            \textcolor{Maroon}{\vdots} & \textcolor{Blue}{\ddots} & \textcolor{OliveGreen}{\vdots} \\
            \textcolor{Maroon}{\la_{d,1}} & \textcolor{Maroon}{\cdots} & \textcolor{Blue}{\la_{d, d}} \\
        \end{pmatrix} \]
        \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} \textcolor{OliveGreen}{R_{m,n}} \textcolor{Maroon}{RP_{n,m}}}} \tcdot \bs{\prod_{l=1}^{d} \textcolor{Blue}{GP_{l}}} \]
        \item Global Phase Terms: \textcolor{Blue}{$GP_{l} = \exp\br{iP_l \lambda_{l,l}}$}
        \item Relative Phase Terms: \textcolor{Maroon}{$RP_{n,m} = \exp\br{i P_n \lambda_{n,m}}$}
        \item Rotation Terms: \textcolor{OliveGreen}{$R_{m,n} = \exp\br{i \si_{m,n} \lambda_{m,n}}$}
        \item Projection Operators: $P_l = \ket{l}\bra{l}$
        \item Anti-symmetric $\si$-matrices: $\si_{m,n} = - i\ket{m}\bra{n} + i \ket{n}\bra{m}$
        \item Parameters $\la_{n,m} \in \bs{0, 2\pi}$
    \end{itemize}
\end{frame}

@@

\begin{frame}
    \frametitle{Maximal Violation}
    \includegraphics[width=\linewidth]{../../figures/distributions/plotted_dist_I_2_max_violation.pdf}
    \[ \text{Relative Violation:} \qquad V_F = \f{\min_P\bc{I\br{P}}}{I\br{P_F}} \]
\end{frame}

>>>>

\begin{frame}
    \frametitle{Inflation Lemma}
    \begin{lemma}[Inflation Lemma]
    Given $\graph = \br{\nodes, \edges}$ and inflation $\graph' = \br{\nodes', \edges'}$:
    \begin{center}
        \begin{tikzpicture}
            \pgfmathsetmacro{\vs}{2.2};
            \pgfmathsetmacro{\hs}{5.2};
            \draw (0*\hs,0*\vs) node[](pn){$\underbrace{\bc{\prob[N] \mid N \in \ImInj[\graph]{\graph'}}}_{\text{compatible with $\graph$}}$};
            \draw (1*\hs,0*\vs) node[](cp){$\bc{\prob[n\mid \Pa[\graph]{n}] \mid n \in \nodes}$};
            \draw (1*\hs,-1*\vs) node[](cp_){$\bc{\prob[n'\mid \Pa[\graph']{n'}] \mid n' \in \nodes'}$};
            \draw (0*\hs,-1*\vs) node[](pn_){$\underbrace{\bc{\prob[N'] \mid N' \in \Inj[\graph]{\graph'}}}_{\text{compatible with $\graph'$}}$};
            \draw[very thick, ->] (pn) -- (cp);
            \draw[very thick, ->] (cp) -- (cp_) node [midway, above, sloped]{{\footnotesize define}};
            \draw[very thick, ->] (cp_) -- (pn_);
        \end{tikzpicture}
    \end{center}
    \end{lemma}
\end{frame}

@@

\begin{frame}
    \frametitle{Parameterizing Unitary Group}
    \begin{itemize}
        \item \cite{Spengler_2010_Unitary} parameterization of $\s{U}\br{d}$
        \[ \la = \begin{pmatrix}
            \textcolor{Blue}{\la_{1,1}} & \textcolor{OliveGreen}{\cdots} & \textcolor{OliveGreen}{\la_{1, d}} \\
            \textcolor{Maroon}{\vdots} & \textcolor{Blue}{\ddots} & \textcolor{OliveGreen}{\vdots} \\
            \textcolor{Maroon}{\la_{d,1}} & \textcolor{Maroon}{\cdots} & \textcolor{Blue}{\la_{d, d}} \\
        \end{pmatrix} \]
        \[ U = \bs{\prod_{m=1}^{d-1} \br{\prod_{n=m+1}^{d} \textcolor{OliveGreen}{R_{m,n}} \textcolor{Maroon}{RP_{n,m}}}} \tcdot \bs{\prod_{l=1}^{d} \textcolor{Blue}{GP_{l}}} \]
        \item Global Phase Terms: \textcolor{Blue}{$GP_{l} = \exp\br{iP_l \lambda_{l,l}}$}
        \item Relative Phase Terms: \textcolor{Maroon}{$RP_{n,m} = \exp\br{i P_n \lambda_{n,m}}$}
        \item Rotation Terms: \textcolor{OliveGreen}{$R_{m,n} = \exp\br{i \si_{m,n} \lambda_{m,n}}$}
        \item Projection Operators: $P_l = \ket{l}\bra{l}$
        \item Anti-symmetric $\si$-matrices: $\si_{m,n} = - i\ket{m}\bra{n} + i \ket{n}\bra{m}$
        \item Parameters $\la_{n,m} \in \bs{0, 2\pi}$
    \end{itemize}
\end{frame}

@@

\begin{frame}
    \frametitle{Maximal Violation}
    \includegraphics[width=\linewidth]{../../figures/distributions/plotted_dist_I_0_max_violation.pdf}
    \[ \text{Relative Violation:} \qquad V_F = \f{\min_P\bc{I\br{P}}}{I\br{P_F}} \]
\end{frame}

\begin{frame}
    \frametitle{Maximal Violation Symmetric}
    \includegraphics[width=\linewidth]{../../figures/distributions/plotted_dist_I_2_max_violation.pdf}
    \[ \text{Relative Violation:} \qquad V_F = \f{\min_P\bc{I\br{P}}}{I\br{P_F}} \]
\end{frame}
